\documentclass[acmsmall,nonacm]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcommand{\highlightBlue}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\highlightRed}[1]{\textcolor{red}{\textbf{#1}}}

\newcommand{\snsMyth}
  {\ensuremath{\textsc{Smyth}}}
\newcommand{\myth}
  {\ensuremath{\textsc{Myth}}}
\newcommand{\leon}
  {\ensuremath{\textsc{Leon}}}
\newcommand{\synquid}
  {\ensuremath{\textsc{Synquid}}}

\newcommand{\experimentTableSize}
  {\scriptsize}
\newcommand{\experimentCaptionSize}
  {\footnotesize}

\newcommand{\vsepBeforeCaption}{\vspace{0.05in}}

\begin{document}

\title{Smyth Experiment Tables}
\subtitle{ICFP 2020 Artifact Evaluation (May 22, 2020)}
\maketitle

\textbf{Changes to \snsMyth{}.}
%
Since the submission, we have made two algorithmic improvements:

\begin{enumerate}

\item Change to search order: trying to synthesize case expressions before
constructors (still subject to the same staging parameters). This change tends
to improve performance and produce more readable solutions for some benchmarks.

\item From Section 6.3: ``Future work should consider how to automatically
reconfigure staging parameters to account for the structure of user-provided
sketches.'' We have implemented such ``responsive'' staging parameters.

\end{enumerate}

We have also since removed the client-side portion of our implementation that
had been written in Elm. The new (command-line) interface is written in OCaml.

\vspace{0.30in}
\noindent
\textbf{Changes to \synquid{}.}
%
From Section 6.4: ``Discussion with the authors of \synquid{} has revealed an
implementation issue involving the axiomatization of recursive
datatypes in the underlying logic.
%
As a result, desired solutions for many benchmarks---even non-recursive
ones---failed to typecheck.
%
When this issue is addressed, \synquid{} may very well synthesize many
of these tasks (conservatively marked \textbf{?}).''

Nadia Polikarpova has recently fixed this issue
%
(\url{https://github.com/nadia-polikarpova/synquid/commit/20e6d62e151e314cc0e5b36983fded12e6e6c8c4}),
%
so we re-ran the \synquid{} experiments.


\vspace{0.30in}
\noindent
\textbf{Updated Figure 10 Results.}
%
As such, our Figure 10 results have changed slightly.
%
The following page replicates Figure 10 from our submission.
%
The rest of the document includes Tables 1, 2, 3, and 4, corresponding to the four
experiments, and describes the differences.

Tables 1, 2, and 3 include a \textit{Revised Artifact (Ours)} column to show our
updated results, using blue highlights to emphasize differences compared to the
\textit{Submission}.
%
The \textit{Revised Artifact (Yours)} column shows the results that you obtained
on your machine; differences from ours are highlighted in red.
%
If you have not run the experiments, the column should be filled with dots.


\vspace{0.30in}
%
\noindent
%
\textbf{\leon{} and \synquid{} Benchmarks (\texttt{experiments/exp-4-logic/}):}
%
For Experiment 4, we wrote a script
%
(\texttt{generate-benchmarks.py})
%
to generate \leon{} and \synquid{} tasks
%
(\texttt{generated/}),
%
which we copied and pasted into the respective web editors.
%
Our labeled results are in \texttt{results/}.
%
The helper script \texttt{show-results.sh} summarizes the labels,
and also includes comments with some shell commands we found useful during
this experiment.
%
The sketching benchmarks we tried (discussed on lines 1033-1034 of the
submission) can be found in \texttt{sketches/}.

\leon{}: If \url{https://leon.epfl.ch/} doesn't work, you might try
\url{https://leon.epfl.ch/}, a URL that Viktor Kuncak provided. In either case,
look for the ``Synthesis'' menu on the right and click ``Search.''

\synquid{}: The web editor \url{http://comcom.csail.mit.edu/comcom/#Synquid}
currently server the version with Nadia's recent changes. Nadia suggested
running our benchmarks with the \texttt{-e=True} flag; we found that
\texttt{-e=False} was needed for a few benchmarks to succeed.

\clearpage

\setcounter{figure}{9}
\input{figure-10-submission}
\setcounter{figure}{0}

\input{table-1}
\input{table-2}
\input{table-3}
\input{table-4}

\end{document}
\endinput
